Topic Modeling of News

### 2018-02-16 paper/R/04_Modelresults.Rmd
from ownership to site

---
title: "Regression"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    toc: true
    toc_float: true
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

@@

# 2. Data 
```{r caching, echo = FALSE}
#load("../output/btw_combined.Rda")
load("../output/btw_comb.Rda")
```

@@

# 3. Model Results
```{r echo = FALSE}
load("../output/models/STM_ownership 40 .Rda")
k <- stmOut$settings$dim$K
```

@@

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition",
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder",
                   7, "political trends in GER", 8, "Merkel vs.Schulz",
                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President",
                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)",
                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg",
                   15, "error (text processing failure)", 16, "Public authorities (police, BKA)",
                   17, "Federal budget statistics", 18, "Family reunion refugees",
                   19, "Election Polls", 20, "AfD in social media", 21, "(Sexual) assaults, Gender Debate, M.Schwesig", 
                   22, "elections in Niedersachsen", 23, "Court judgements (on terror attacks, NSU)", 
                   24, "election campaigns & political talkshows", 25, "German armed forces",
                   26, "Issues in the Bundestag", 27, "C.Lindner FDP", 28, "Diplomatic relations w Turkey & Russia", 
                   29, "A.Merkel in east GER", 30, "H.Kohl obituary", 31, "AfD (Petri, Gauland, Höcke)", 
                   32, "Refugees (in GER)", 33, "EU policies", 34, "DIE LINKE", 35, "SPD", 
                   36, "Islam and antisemitism in GER", 37, "AfD in parliament", 38, "Church", 
                   39, "Terror attack in Berlin (Amri)", 40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)

# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)",
#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
#                    7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
#                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
#                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
#                    12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
#                    15, "error (text processing failure)", 16, "Refugees in GER", 
#                    17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
#                    19, "Polls federal election", 20, "AfD in social media", 
#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
#                    23, "Court judgements on terrorist attacks", 24, "election campaigns & political talkshows", 
#                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
#                    28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)

@@

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==16) %>% select(title, gamma, site) %>%
  arrange(desc(gamma)) %>%
  htmlTable::htmlTable(align="l")
```

@@

Create a Df that contains the columns means of theta (per topic and covariate level)
```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(ownership=stmOut$settings$covariates$yvarlevels,
           topic = 1)

for(i in 2:k) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(ownership=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

  freq <- rbind(freq, freq1)
}
```

@@

p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))
```

@@

### by ownership
```{r}
plotNewspaperHistogram(2)
```

@@

```{r}
freq1 <- freq %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic") %>%
  left_join(., frequency %>% mutate(topic_name = topic) %>%
              select(-topic),
            by = "topic_name")

p2 <- ggplot(freq1, aes(reorder(topic_name,frequency), freq_diff,
                 fill = factor(value))) +
  geom_col(show.legend = F) +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(axis.text.y = element_blank(),
          #axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

p1 + p2

ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
dpi = 600)
```

```{r fig.height=6}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[7,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[7,], collapse="\n")))
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~ownership+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
```

@@

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("ownership", "", parameter),
         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

```{r}
#sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")
sites <- c("(Intercept)", "public", "private")
p1 <- coeff %>% 
  #filter(parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
dpi = 600)
```

## 3.3 Topic Correlation
```{r}
## Create Dataframe with correlations
cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:k

df <- as.data.frame(cor) %>% 
  mutate(topic = 1:k) %>%
  melt(., id="topic", value.name="corr") %>%
  mutate(site = stmOut$settings$covariates$yvarlevels[1])

for (i in 2:2) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:k

  df1 <- as.data.frame(cor) %>%
    mutate(topic = 1:k) %>%
    melt(., id="topic", value.name="corr") %>%
    mutate(site = stmOut$settings$covariates$yvarlevels[i])

  df <- rbind(df,df1)
}
```

```{r}
df <- df %>% 
  left_join(.,topics.df, by = "topic") %>%
  mutate(topic1 = topic,
         topic_name1 = topic_name,
         topic = as.numeric(variable)) %>%
  select(-topic_name) %>%
  left_join(., topics.df, by="topic")
```

```{r}
p1 <- df %>%
  filter(corr>0.05 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

# ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

### Network graph
```{r}
i <- 1
cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
cormat <- ifelse(cormat >=0.05, cor, 0)
# 
g <- igraph::simplify(igraph::graph.adjacency(cormat, mode = "undirected", weight=TRUE))
igraph::V(g)$name <- topics.df$topic_name
igraph::V(g)$props <- colMeans(stmOut$theta)

p1 <- topicCorrNetwork(g, stmOut$settings$covariates$yvarlevels[i])
# 
ggsave(
      paste0("../figs/corrplot",i,".png"),
      p1,
      dpi = 300,
      width = 9,
      height = 6
    )
```

### Overlapping Correlation
Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot. Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
```{r}
png("../figs/overlapping_correlation.png")
topicCorrCompare(1,5)
dev.off()
```

>>>>

---
title: "Model Results"
subtitle: ""
author: "Franziska Löw"
date: ""
output: 
  html_document:
    theme: "lumen"
    highlight: "tango"
    code_folding: show
    self_contained: true
---

@@

# 2. Data 
```{r caching, echo = FALSE}
load("../output/btw_out.Rda")
```

@@

# 3. Model Results
```{r echo = FALSE}
load("../output/models/STM 35 .Rda")
k <- stmOut$settings$dim$K
```

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
                   5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 
                   9, "AfD in Parliament", 10, "A.Merkel", 11, "Deportation, radicalization, refugees", 
                   12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs. Söder", 
                   15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 
                   19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 
                   22, "German armed forces, Mali", 23, "Nuclear Waste, Weather reports", 
                   24, "Innenministerium, Verfassungsschutz", 
                   25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 
                   28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 
                   32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 
                   35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)

@@

### now we can inspect the unclear topics
```{r}
btw.2 %>% filter(topic==23) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  htmlTable::htmlTable(align="l")
```

@@

@@

p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

p1
```

@@

### by site
```{r}
plotNewspaperHistogram(11)
```

Create a Df that contains the columns means of theta (per topic and covariate level)
```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(site=stmOut$settings$covariates$yvarlevels,
           topic = 1)

for(i in 2:k) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(site=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

  freq <- rbind(freq, freq1)
}

freq <- freq %>%
  left_join(., topics.df, by = "topic") %>%
  mutate(topic = topic_name) %>%
  left_join(., frequency %>% select(topic, frequency),
            by = "topic")
```

@@

```{r}
ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
  geom_col(fill = col[1]) +
  #scale_fill_manual(values = col[1]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7)
  theme(axis.text.y = element_blank(),
          #axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

p2

# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
# dpi = 600)
```

```{r fig.height=11, fig.width=5}
topic <- 11

plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~site+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
```

@@

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

```{r}

p1 <- coeff %>% 
  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
# dpi = 600)
```

### 2018-02-16 paper/R/backup.Rmd
from ownership to site

>>>>

## 3.3 Topic Correlation
```{r}
## Create Dataframe with correlations
cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:k

df <- as.data.frame(cor) %>% 
  mutate(topic = 1:k) %>%
  melt(., id="topic", value.name="corr") %>%
  mutate(site = stmOut$settings$covariates$yvarlevels[1])

for (i in 2:2) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:k

  df1 <- as.data.frame(cor) %>%
    mutate(topic = 1:k) %>%
    melt(., id="topic", value.name="corr") %>%
    mutate(site = stmOut$settings$covariates$yvarlevels[i])

  df <- rbind(df,df1)
}
```

```{r}
df <- df %>% 
  left_join(.,topics.df, by = "topic") %>%
  mutate(topic1 = topic,
         topic_name1 = topic_name,
         topic = as.numeric(variable)) %>%
  select(-topic_name) %>%
  left_join(., topics.df, by="topic")
```

```{r}
p1 <- df %>%
  filter(corr>0.05 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  #scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

p1

# ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
# dpi = 600)
```

### Network graph
```{r}
i <- 1
cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
cormat <- ifelse(cormat >=0.05, cor, 0)
# 
g <- igraph::simplify(igraph::graph.adjacency(cormat, mode = "undirected", weight=TRUE))
igraph::V(g)$name <- topics.df$topic_name
igraph::V(g)$props <- colMeans(stmOut$theta)

p1 <- topicCorrNetwork(g, stmOut$settings$covariates$yvarlevels[i])
# 
ggsave(
      paste0("../figs/corrplot",i,".png"),
      p1,
      dpi = 300,
      width = 9,
      height = 6
    )
```

### Overlapping Correlation
Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot. Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
```{r}
png("../figs/overlapping_correlation.png")
topicCorrCompare(1,5)
dev.off()
```
